Decade of Lost Precision: A General Framework For Image Feature Matching Without Geometric Constraints

### 2014-10-14 paper.tex
Removed Sabine as Author
Made a few aestethic changes

\documentclass[]{elsarticle}

@@

\end{document}
\section{Introduction}
%
Matching image points is a crucial ingredient in almost all computer vision applications that deal with sparse local image features, such as image categorization \cite{bosch2008scene}, image stitching \cite{brown2007automatic}, object detection \cite{zhang2007local}, and near duplicate detection \cite{zhao2009scale}, to mention just a few examples.  All of these rely on accurately finding the correspondence(s) of a point on an object in a \emph{query image} given one or more \emph{target images} that might contain the same object.  In many applications the \emph{target images} have undergone transformations with respect to the \emph{query image}; in stereo vision, the viewpoint is different, while in object recognition and near duplicate  detection both the lighting and even the object itself may also be transformed.

@@

A plethora of solutions have combined ratio match with various geometric constraints to improve matching. These constraints are based on assumptions regarding the transformation between the query and \emph{target images}. At the stricter end we have epipolar constraints assuming that the images can be tied by a homography \cite{torr2000mlesac, chum2005matching} and angular constraints assuming the correspondences are angled similarly \cite{kim2008efficient, schmid1997local}. Often these approaches are made computationally feasible by modeling the case of feature correspondences as an instance of graph matching, where each feature is a vertex, and edge values correspond to a geometric relation between two features. In this case approximate graph matching algorithms can be used to efficiently establish an isomorphism between the graph of features in two images \cite{leordeanu2005spectral, torresani2008feature, yarkony2010covering}. Others define image regions and reject or accept correspondences based on the regions they connect \cite{cho2009feature, wu2011robust}.

@@

To make further discussion easier we introduce the following nomenclature:
\begin{itemize}
\item{Let $f_q$ be any feature point in the \emph{query image} that we 
    are currently trying to match}.
\item{Let $F$ be a set of features. $F_{t}$ for example is the set 
    of features from the \emph{target image}}.
\item{Let $\tau \in [0 \ldots 1]$ be a threshold used to decide whether 
    to keep a match or discard it.} %We keep a match only if it has a \emph{uniqueness ratio} lower than $\tau$}
\item{Let the \emph{proposed match} be the nearest neighbor of the query 
    feature $f_q$ picked from a set of feature points that we will call 
the \emph{proposal set} which does not contain the query feature itself}.
\item{Let the \emph{baseline match} be the nearest neighbor of the query 
    feature $f_q$ picked from a set of feature points that we will call 
the \emph{baseline set} which neither contains the \emph{proposed match} 
nor the query feature}.
\end{itemize}

@@

Algorithm~\ref{alg-gen} shows the generalized matching framework where the \emph{proposal set} and \emph{baseline set} are defined according to Figure~\ref{fig:overview}.  In practice for e.g.\ \emph{Ratio-Match} we can obtain $f_p$ and $f_b$ by finding the two nearest neighbors of $F_{t}$. The other algorithms can be optimized similarly. Figure~\ref{fig:matching} illustrates the structure of this algorithm.

@@

\section*{References}
\bibliographystyle{elsarticle-num}
\bibliography{bibliography}

>>>>

\documentclass[review]{elsarticle}

@@

\section{Introduction}
%
Matching image points is a crucial ingredient in almost all computer vision applications that deal with sparse local image features, such as image categorization \cite{bosch2008scene}, image stitching \cite{brown2007automatic}, object detection \cite{zhang2007local}, and near duplicate detection \cite{zhao2009scale}, to mention just a few examples.  All of these rely on accurately finding the correspondence(s) of a point on an object in a \emph{query image} given one or more \emph{target images} that might contain the same object.  In many applications the \emph{target images} have undergone transformations with respect to the \emph{query image}; in stereo vision, the viewpoint is different, while in object recognition and near duplicate  detection both the lighting and even the object itself may also be transformed.

@@

A plethora of solutions have combined ratio match with various geometric constraints to improve matching. These constraints are based on assumptions regarding the transformation between the query and \emph{target images}. At the stricter end we have epipolar constraints assuming that the images can be tied by a homography \cite{torr2000mlesac, chum2005matching} and angular constraints assuming the correspondences are angled similarly \cite{kim2008efficient, schmid1997local}. Often these approaches are made computationally feasible by modeling the case of feature correspondences as an instance of graph matching, where each feature is a vertex, and edge values correspond to a geometric relation between two features. In this case approximate graph matching algorithms can be used to efficiently establish an isomorphism between the graph of features in two images \cite{leordeanu2005spectral, torresani2008feature, yarkony2010covering, yuan2012efficient}. Others define image regions and reject or accept correspondences based on the regions they connect \cite{cho2009feature, wu2011robust}.

@@

To make further discussion easier we introduce the following nomenclature:
\begin{itemize}
\item{Let $f_q$ be a feature point in the \emph{query image}}.
\item{Let $F$ be a set of features. $F_{t}$ denotes all
        features from the \emph{target image}}.
\item{Let $\tau \in [0 \ldots 1]$ be a threshold used to decide whether 
    to keep a match.} %We keep a match only if it has a \emph{uniqueness ratio} lower than $\tau$}
\item{Let the \emph{proposed match} be the nearest neighbor of the query 
    feature $f_q$ picked from a set of feature points that we will call 
the \emph{proposal set} which does not contain the query feature itself}.
\item{Let the \emph{baseline match} be the nearest neighbor of the query 
    feature $f_q$ picked from a set of feature points that we will call 
the \emph{baseline set} which neither contains the \emph{proposed match} 
nor the query feature}.
\end{itemize}

@@

Algorithm~\ref{alg-gen} shows the generalized matching framework where the \emph{proposal set} and \emph{baseline set} are defined according to Figure~\ref{fig:overview}. Figure~\ref{fig:matching} illustrates the structure of this algorithm.

@@

\section*{References}
\bibliographystyle{elsarticle-num}
\bibliography{bibliography}
\end{document}
